Colonies - Compute Continuums across Platforms

### 2023-04-02 paper_2023/paper.tex
wip

\section{Related work}
Workflow management has been extensively studied in both academic and industrial settings \cite{apache_airflow}, with numerous approaches proposed to address the challenges in this field. For instance, Apache Airflow \cite{apache_airflow} is a popular open-source workflow management system for handling data engineering pipelines. Like Colonies, Apache Airflow enables developers to create custom operators and executors that can be integrated with various systems. Additionally, Apache Airflow offers an HTTP API that allows for the development of clients and software development kits (SDKs) in multiple programming languages.

However, Apache Airflow is not designed around a queuing system. Instead, it must be integrated with a message broker, such as RabbitMQ \cite{rabbitmq} or Kafka \cite{apache_kafka}, to implement task queues, resulting in a more complex architecture than Colonies. Furthermore, Colonies is based on a distributed microservice architecture that makes it more suitable for DevOps software development. As Colonies is loosely coupled, executors can be implemented and dynamically deployed without reconfiguring the workflow engine, effectively transforming it into a grid computing platform.

When it comes to academic works, \cite{GarciaRepresa1740746} t

@@

Queues can be implemented in different ways, and while message brokers are a common solution, Colonies has adopted an alternative strategy by leveraging a standard database and querying it for tasks to assign to different executors. One key advantage of this approach is that it enables fine-grained task assignments, making it possible to assign specific tasks to particular executors. For instance, an executor of the browser type can be limited to only executing tasks of the browser type. This level of granularity cannot easily be implemented using message brokers which generally do not offer introspection of queue, or provide the ability to pull specific messages out of the queue. Generarally, the only way to retrieve a specific message is to pull all messages from the queue, obtain the message, and then place all remaining messages back into the queue in the same order. In contrast, a database can also function as a queue and a query can match any columns thus making it possible to assign specific executors to processes.

@@

Incorporating Raft into the Colonies framework allows incoming assign requests to be directed towards the leading Colonies server, ensuring that only one Colonies server replica handles these requests. Figure \ref{fig:ha_deployment} shows an overview of a high-availability Colonies deployment. A new leader is elected in the event that a Colonies server replica fails. The Raft protocol also enables seamless updates to the Colonies server software by making it possible to upgrade each replica individually. As a result, Colonies becomes well-suited for Kubernetes deployments.

>>>>

\section{Related work}
Workflow management has been extensively studied in both academic and industrial settings with numerous approaches proposed to address the challenges in this field. For example, Apache Airflow \cite{apache_airflow} is a popular open-source workflow management system for handling data engineering pipelines. Like Colonies, Apache Airflow enables developers to create custom operators and executors that can be integrated with various systems. Additionally, Apache Airflow offers an HTTP API that makes it possible to develop software development kits (SDKs) in various programming languages. However, Apache Airflow does not realy on a queuing system. Instead, it must be integrated with a message broker, such as RabbitMQ \cite{rabbitmq} or Kafka \cite{apache_kafka}, to implement task queues, resulting in a more complex architecture than Colonies. Furthermore, Colonies is based on a distributed microservice architecture that makes it more suitable for DevOps software development. As Colonies is loosely coupled, executors can be implemented and dynamically deployed without reconfiguring the workflow engine, effectively making it work like a grid computing platform.

Argo is a ...

OpenWolf \cite{openwolf} is a serverless workflow engine designed to utilize the Function-as-a-Service (FaaS) paradigm for composing complex scientific workflows. It is based on OpenFaaS \cite{openfaas}, which allows functions to run on Kubernetes clusters. In contrast, Colonies does not require Kubernetes, but provides a zero-trust security protocol to allow functions to be executed securely by distributed executor workers deployed anywhere on the Internet.

The serverless workflow project \cite{serverlessworkflow} aims at providing a vendor-neutral workflow DSL. Synapse is a workflow management system implementing the serverless workflow specification. It is important to point out that Colonies does not provide an infrastructure for function execution. Instead, Colonies primary role is to serve as a platform for coordinating function executions, which are carried out by distributed executor services.

Colonies is based on a microservice architecture. J. Represa et al. \cite{GarciaRepresa1740746} discusses various challenges developing microservice-based workflow management for industrial automation. They concludes that microservice-based workflow technologies is feasible for industrial usage, especially considering its flexibility. The main contribution of this paper is a technica

SCAFE: A Service-Centered Cloud-Native Workflow Engine Architecture

https://www.alibabacloud.com/product/serverless-workflow
https://serverlessworkflow.io/

https://github.com/serverlessworkflow/synapse

AWS Step Functions to design and run a serverless workflow that coordinates multiple AWS Lambda functions.

@@

Queues can be implemented in different ways, and while message brokers are a common solution, Colonies adopts an alternative strategy and leverage a standard database and querying it for tasks to assign to different executors. One key advantage of this approach is that it enables fine-grained task assignments, making it possible to assign specific tasks to particular executors. For instance, an executor of the browser type can be limited to only executing tasks of the browser type. This level of granularity cannot easily be implemented using message brokers which generally do not offer introspection of queue, or provide the ability to pull specific messages out of the queue. Generarally, the only way to retrieve a specific message is to pull all messages from the queue, obtain the message, and then place all remaining messages back into the queue in the same order. In contrast, a database can also function as a queue and a query can match any columns thus making it possible to assign specific executors to processes.

@@

Integrating Raft with the Colonies framework allows incoming assign requests to be directed towards the leading Colonies server, thereby ensuring that only one Colonies server replica handles such requests. Figure \ref{fig:ha_deployment} shows an overview of a high-availability Colonies deployment. A new leader is elected in the event that a Colonies server replica fails. The Raft protocol also enables seamless updates to the Colonies server software by making it possible to upgrade each replica individually. As a result, Colonies becomes well-suited for Kubernetes deployments.
